---
title: "UO Happiness Retreat Outcome Survey"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

<style type="text/css">

.sidebar {
  font-size: 1.5rem
}

</style>


```{r setup, include=FALSE}
library(flexdashboard)
library("dplyr")
library("tidyverse")
library("rio")
library("here")
library("forcats")
library("fivethirtyeight")
library("wesanderson")
library("ggplot2")
library("gdata")
library("viridis")
library("colorblindr")
library("stringr")
library("tidytext")
library("kableExtra")
library("formattable")
library("flextable")
library(fcuk)
library(emojifont)
library(devtools)

theme_set(theme_minimal(base_size = 8))
```

# Demographics {data-icon="fa-users"} 

Sidebar Title {.sidebar}
--------
With the help of my reviewer, I was able to achieve this version of the final plot. Looking at the previous versions, some of the unaesthetic visualization elements include: unnessasary axes descriptions, lack-of-detailed title, color-blind unfriendly, x-y axes lines going over the bars, heavy cognitive load.


Column {.tabset}
-----------------------------------------------------------------------


### Final Version

```{r participants1}
SKY <- import(here("data", "survey.xlsx"), setclass = "tbl_df") 

OH0 <- SKY %>% 
  group_by(Category, Gender) %>% 
  summarise(n=n()) 
  
ggplot(OH0, aes(x = fct_reorder(Category, n), n)) +
  geom_col(aes(fill = Gender),
           color = "white",
           alpha = 0.7) +
  scale_y_continuous(breaks = seq(0, 11, by = 1),
                     limits = c(0, 10.25)) +
  scale_fill_OkabeIto() +
  coord_flip(expand = FALSE) +
  labs(x = "",
       y = "Number of participants",
       title = "Participant Distribution") +
  theme_minimal(base_size = 15)  + 
  theme(panel.grid.minor = element_line(linetype = "blank")) +
  guides(fill = "none")+
  geom_text(data=OH0[1,], aes(label=Gender), hjust=0)+
  geom_text(data=OH0[2,], aes(label=Gender), hjust =2)

```


### Version 3
```{r participants2}
SKY %>% 
  count(Category) %>% 
  ggplot(aes(x = fct_reorder(Category, n), n)) +
  geom_col(aes(fill = Category),
           color = "white",
           alpha = 0.7) +
  scale_y_continuous(breaks = seq(0, 11, by = 1),
                     limits = c(0, 10.25)) +
  scale_fill_OkabeIto() +
  coord_flip(expand = FALSE) +
  labs(x = "Category",
       y = "Count",
       title = "Where are the participants from?") +
  theme_minimal(base_size = 15)  + 
  theme(panel.grid.minor = element_line(linetype = "blank")) +
  guides(fill = "none")
```

### Version 2
```{r participants3}
SKY %>% 
  mutate(Category = factor(Category, 
                           levels = c("Graduate",
                                      "Community member", 
                                      "Faculty/Staff",
                                      "Undergrad",
                                      "Post-bach"))) %>% 

ggplot(aes(x = Category)) +
  geom_histogram(stat = "count",
                 color = "white",
                 alpha = 0.7) +
  scale_y_continuous(breaks = seq(0, 11, by = 1)) +
  scale_fill_OkabeIto() +
  coord_flip() +
  labs(x = "Category",
       y = "Count",
       title = "Where are the participants from?") +
    theme_minimal(base_size = 15)  + 
  theme(panel.grid.minor = element_line(linetype = "blank"))
```

### Version 1
```{r participant4}
ggplot(SKY, aes(x = Category)) +
  geom_histogram(stat = "Count",
                 fill = "#56B4E9",
                 color = "white",
                 alpha = 0.7) +
   theme_minimal(base_size = 15)
```


# Recommend {data-icon="fa-thumbs-up"} 

Sidebar Title {.sidebar}
--------
Version 1 was basically a `r emo::ji("vomit")` (aka train-wrack). Later, a more presentatble visualization, a one without unnecessary load of cognition surfaced. 


Column {.tabset}
-----------------------------------------------------------------------

### Final Version
```{r recommend1}

SKY <- import(here("data", "survey.xlsx"), setclass = "tbl_df") 

ggplot(SKY, aes(Recommend)) +
  geom_dotplot(aes(fill = Category), 
               stackgroups = TRUE,
               binwidth = .4) +
  scale_fill_OkabeIto(name = "") +
  scale_x_continuous(breaks = 0:6, limits = c(0, 6),
                     labels=c("0" = "", 
                              "1" = "Strongly Disagree",
                              "2" = "Disagree", 
                              "3" = "Neutral",
                              "4" = "Agree", 
                              "5" = "Strongly Agree",
                              "6" = "")) +
  scale_y_continuous(labels=c("0.00" = "0", 
                              "0.25" = "6",
                              "0.50" = "12", 
                              "0.75" = "18",
                              "1.00" = "24")) +
   coord_flip(expand = FALSE) +
   theme_minimal(base_size = 15) +
  theme(panel.grid.minor = element_line(linetype = "blank")) +
  labs(x = NULL, 
       y = NULL, 
       title = "Here is how the participants feel about",
       subtitle = "recommending this Retreat to their peers")+
  labs(y = "Number of Participants") +
  theme(legend.position = "bottom")
```

### Version 2
```{r recommend2}
ggplot(SKY, aes(Recommend)) +
  geom_dotplot(aes(fill = Category), 
               stackgroups = TRUE,
               binwidth = 0.3) +
  scale_fill_OkabeIto() +
  scale_x_continuous(breaks = 0:6, limits = c(0, 6),
                     labels=c("0" = "", 
                              "1" = "Strongly Disagree",
                              "2" = "Disagree", 
                              "3" = "Neutral",
                              "4" = "Agree", 
                              "5" = "Strongly Agree",
                              "6" = "")) +
  scale_y_continuous(labels=c("0.00" = "0", 
                              "0.25" = "6",
                              "0.50" = "12", 
                              "0.75" = "18",
                              "1.00" = "24")) +
   coord_flip() +
   coord_flip(expand = FALSE) +
   theme_minimal(base_size = 15) +
  theme(panel.grid.minor = element_line(linetype = "blank")) +
  labs(x = NULL, 
       y = NULL, 
       title = "I would recommend this training to my peers as they would benefit",
       subtitle = "N = 21")+
  labs(y = "Number of Participants")
```

### Version 1
```{r recommend3}
ggplot(SKY, x = 0:5, aes(Recommend, Category)) +
   ggridges::geom_density_ridges(color = "white",
                                alpha = 0.4) +
  scale_color_OkabeIto() +
    labs(x = "Strongly Disagree - Strongly Agree",
       y = "Category",
       title = "I would recommend this training to my peers as they would benefit from it")  +
  theme_minimal(base_size = 15)
```



# More {data-icon="fa-grin-stars"} 

Sidebar Title {.sidebar}
--------
Initially, I plotted all of participant responses into individual dotplots. Looing at them, I don't know how much information I gained. So, I decided to try the table. The final table has the approprate title and everything. 
`r emo::ji("star")` `r emo::ji("star2")` `r emo::ji("star")` A little victory. 

Column {.tabset}
-----------------------------------------------------------------------

### Final Version
```{r table}
# SKY %>%
#   count(energy) %>%
#   mutate(prop = 100*n/sum(n-1)) 
# 
# SKY %>%
#   count(clarity_mind) %>%
#   mutate(prop = 100*n/sum(n-1))
# 
# SKY %>%
#   count(multiple_responsibilities) %>%
#   mutate(prop = 100*n/sum(n-1))
#   
# SKY %>%
#   count(connect_to_myself) %>%
#   mutate(prop = 100*n/sum(n-1))
# 
# SKY %>%
#   count(stay_focused) %>%
#   mutate(prop = 100*n/sum(n-1))
# 
# SKY %>%
#   count(remain_calm) %>%
#   mutate(prop = 100*n/sum(n-1))
# 
# SKY %>%
#   count(gain_resilience) %>%
#   mutate(prop = 100*n/sum(n-1))
# 
# 
# SKY %>%
#   count(broader_perspectives) %>%
#   mutate(prop = 100*n/sum(n-1))
# 
# SKY %>%
#   count(connect_with_others) %>%
#   mutate(prop = 100*n/sum(n-1))

SKY2 <- import(here("data", "SKY2.xlsx"), setclass = "tbl_df") 

SKY2 %>% 
  kable(caption = "The SKY Happiness Retreat impacts various domains of life") %>% 
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", full_width = NULL, position = "left")) %>% 
  column_spec(6:6, bold = T, color = "#3A9E23", background = "#F8F668") %>%
   footnote(general = "The participants were asked to rate how the techniques taught in the SKY Happiness Retreat have the ability to impact different areas.",
            number = c("Numbers are in percentage"))

```


### Final to last
```{r table2}
SKY2 %>% 
  kable() %>% 
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", full_width = NULL, position = "left")) %>% 
  column_spec(6:6, bold = T, color = "#3A9E23", background = "#F8F668") %>%
   footnote(general = "The participants were asked to rate how the techniques taught in the SKY Happiness Retreat have the ability to impact different areas.",
            number = c("Numbers are in percentage"))
```

### Version 1
```{r table1}
Fig3.1 <- ggplot(SKY, aes(x = Name, y = energy)) +
   geom_point() +
  coord_flip() +
  labs(x = "Participant",
       y = "Strongly Disagree - Strongly Agree",
       title = "The Retreat has increased my energy levels") +
    theme_minimal(base_size = 15)
Fig3.1 + ylim(0, 5)

```

# Experience {data-icon="fa-crown"} 

Sidebar Title {.sidebar}
--------
It's cool to analyze qualitative data with R. The final-final plot: the code is hidden, x-y axes lines don't go over the bars, lables and title are updated. 


Column {.tabset}
-----------------------------------------------------------------------


### Final final (fingers-crossed)
```{r f}

experience <- c("I thought it was positive and powerful",
                "It was very beautiful. It felt like truth",
                "Fantastic growth experience",
                "Wonderful! There were physically challenging moments while sitting for Sudarshan Kriya but I benefited a lot & have smiled more during this retreat than I have in a month",
                "I had a wonderful experience. I had been feeling very unbalanced and uncertain. I now feel much better and more centered",
                "I feel empowered and enlightened",
                "Very positive! Uplifting. Beautiful. Meaningful",
                "Great! I feel more relaxed, confident & can concentrate more on what I am doing",
                "So positive! I feel more capable of managing the things that come my way, and more open to others",
                "It was enlightening and freeing",
                "It was completely transformative. I LOVED it and felt so grateful for Sarah and Ting-fen and all their knowledge",
                "Wonderful!",
                "Kind. Open. Good experience",
                "Very positive, nurturing, and invigorating",
                "Nice. Learned so many new things",
                "Very positive and good use of time",
                "Amazing! So calming, welcoming, and educational",
                "Pretty amazing",
                "Amazing",
                "I enjoyed it",
                "It was great")

experience_df <- tibble(line = 1:21, text = experience)

experience_df <- experience_df %>%
  unnest_tokens(word, text)

data(stop_words)

experience_df <- experience_df %>%
  anti_join(stop_words) %>% 
  filter(word != "feel" & word != "experience")
# 
# experience_df %>%
#   count(word, sort = TRUE) 


experience_df  %>%
  count(word, sort = TRUE) %>%
  filter (n > 1) %>%
  mutate(word = str_to_title(word),
         word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col(fill = "cornflowerblue",
           alpha = 0.7) +
  scale_y_continuous(breaks = seq(0, 11, by = 1),
                     limits = c(0, 5.25)) +
  xlab(NULL) +
  coord_flip() + 
  coord_flip(expand = FALSE) +
  labs(x = "",
       y = "Word Frequency Count",
       title = "How was the experience?") +
    theme_minimal(base_size = 15)  + 
    theme_minimal(base_size = 15)  + 
  theme(panel.grid.minor = element_line(linetype = "blank")) +
  guides(fill = "none") 
```



### Final Version
```{r qualitative}

experience <- c("I thought it was positive and powerful",
                "It was very beautiful. It felt like truth",
                "Fantastic growth experience",
                "Wonderful! There were physically challenging moments while sitting for Sudarshan Kriya but I benefited a lot & have smiled more during this retreat than I have in a month",
                "I had a wonderful experience. I had been feeling very unbalanced and uncertain. I now feel much better and more centered",
                "I feel empowered and enlightened",
                "Very positive! Uplifting. Beautiful. Meaningful",
                "Great! I feel more relaxed, confident & can concentrate more on what I am doing",
                "So positive! I feel more capable of managing the things that come my way, and more open to others",
                "It was enlightening and freeing",
                "It was completely transformative. I LOVED it and felt so grateful for Sarah and Ting-fen and all their knowledge",
                "Wonderful!",
                "Kind. Open. Good experience",
                "Very positive, nurturing, and invigorating",
                "Nice. Learned so many new things",
                "Very positive and good use of time",
                "Amazing! So calming, welcoming, and educational",
                "Pretty amazing",
                "Amazing",
                "I enjoyed it",
                "It was great")

experience_df <- tibble(line = 1:21, text = experience)

experience_df <- experience_df %>%
  unnest_tokens(word, text)

data(stop_words)

experience_df <- experience_df %>%
  anti_join(stop_words) %>% 
  filter(word != "feel" & word != "experience")

experience_df %>%
  count(word, sort = TRUE) 


experience_df  %>%
  count(word, sort = TRUE) %>%
  filter (n > 1) %>%
  mutate(word = str_to_title(word),
         word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col(fill = "cornflowerblue",
           alpha = 0.7) +
  scale_y_continuous(breaks = seq(0, 11, by = 1),
                     limits = c(0, 5.25)) +
  xlab(NULL) +
  coord_flip() + 
  coord_flip(expand = FALSE) +
  labs(x = "",
       y = "Word Frequency Count",
       title = "How was the experience?") +
    theme_minimal(base_size = 15)  + 
    theme_minimal(base_size = 15)  + 
  theme(panel.grid.minor = element_line(linetype = "blank")) +
  guides(fill = "none") 
```



### Version 2
```{r experience2}
experience_df  %>%
  count(word, sort = TRUE) %>%
  filter (n > 1) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col(fill = "cornflowerblue",
           alpha = 0.7) +
  scale_y_continuous(breaks = seq(0, 11, by = 1),
                     limits = c(0, 5.25)) +
  xlab(NULL) +
  coord_flip() + 
  coord_flip(expand = FALSE) +
  labs(x = "Word Use",
       y = "Frequency Count",
       title = "How was the experiece?") +
    theme_minimal(base_size = 15)  + 
    theme_minimal(base_size = 15)  + 
  theme(panel.grid.minor = element_line(linetype = "blank")) +
  guides(fill = "none")
```

### Version 1
```{r V2}
experience_df  %>%
  count(word, sort = TRUE) %>%
  filter (n > 1) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
    theme_minimal(base_size = 15)
```





